\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.2in,right=0.4 in,bottom=0.2in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jaylan Lee} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+31 6 363 820 34 \\ Amersfoort, NL} 
\address{\href{jaylan2993@gmail.com}{jaylan2993@gmail.com} \\ \href{https://www.linkedin.com/in/jaylan-lee-b77694199/}{linkedin.com/in/jaylan-lee-b77694199/} \\ \href{https://github.com/djeelun}{github.com/djeelun}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

% \begin{rSection}{OBJECTIVE}
%
% {Graduate student, seeking positions to gain experience in security-critical environments.}
%
%
% \end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Master of Computer Science}, TU Delft \hfill {2023 - 2025}\\
Specialization in Cybersecurity. Special interest in Quantum Information.\\
Completed thesis with 8.5/10.

{\bf Bachelor of Computer Science}, Utrecht University \hfill {2020 - 2023}\\
Graduated Magna Cum Laude at age 19.\\
Data structures: 10/10. Cryptography: 9.9/10.\\
2nd place $\mu$-hackathon.

{\bf Secondary Education}, 't Hooghe Landt College \hfill {2014 - 2020}\\
Gymnasium / Technasium. (Highest level of Dutch secondary education)\\
Mathematics: 9/10.


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}


\textbf{Teaching Assistant Cryptography} \hfill Sep 2022 - Jan 2023\\
Utrecht University \hfill \textit{Utrecht, NL}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Provided academic support in Cryptography to $>$100 students.
    \item Led discussions, graded assignments, and held office hours.
 \end{itemize}
 
\textbf{Freelance Developer} \hfill Jan 2020 - Jan 2023\\
QuickCode % \hfill \textit{San Francisco, CA}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Web development using React.js, Next.js, Tailwind.css, and more.
     \item Experience developing code in a team, acquired effective communication skills.
 \end{itemize}

\textbf{Labelling datasets for AI using Amazon SageMaker} \hfill Feb 2021 - Nov 2021\\
Octo \hfill \textit{The Hague, NL}
 % \begin{itemize}
 %    \itemsep -3pt {} 
 % \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}

\item \textbf{Post-quantum secure blockchain.} {\textit{Master's thesis.} Implemented \underline{smart contract} modules in C++ for Hyperledger Fabric in order to secure against potential quantum threats.}

\item \textbf{Critical NTP pool hack.} {\textit{Hacking Lab course @ TU Delft.} Demonstrated \underline{severe vulnerability} in NTP Pool. Wrote script to serve arbitrary timestamps to clients requesting times from NTP servers (widely used cluster of time servers). Script can be found at \href{https://github.com/djeelun/malicious-ntpserver}{djeelun/malicious-ntpserver}.}

\item \textbf{DAO for a Secure Software Ecosystem.} {\textit{Bachelor's thesis.} Built a Distributed Autonomous Organization on the \underline{Polygon} blockchain network using \underline{Solidity}. Also contributed novel plugin techniques to the Aragon DAO community, using Diamond Patterns. \underline{Awarded 2nd place} at DAO Global Hackathon. \href{https://docs.secureseco.org/}{SecureSECO DAO}.}
\end{rSection} 

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & Experience writing code in C++, C, C\#, Java, Javascript, Typescript, Python, Haskell \\
Database Skills & Experience with both SQL and NoSQL environments. \\
Soft Skills & Experience using SCRUM and developing AGILE.
\\
\end{tabular}\\
\end{rSection}


%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} 
\begin{itemize}
    \item Participated in PlaidCTF 2025, BreachCTF 2025, Hackathon VU CTF 2025
    \item	Experience in low-level programming (C, asm) graphic calculator.
    \item	Volunteering for Digital Hulpplein Amersfoort, assisting (senior) citizens with questions regarding digital devices.
    % \item	Classically trained pianist
    % \item Operating systems enthousiast.
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
% \begin{rSection}{Leadership} 
% \begin{itemize}
%     \item Admin for the \href{https://discord.com/invite/WWbjEaZ}{FAANGPath Discord community} with over 6000+ job seekers and industry mentors. Actively involved in facilitating online events, career conversations, and more alongside other admins and a team of volunteer moderators! 
% \end{itemize}
%
%
% \end{rSection}


\end{document}
